\documentclass{letter}
\pagestyle{empty}

\begin{document}

\address{Andreas Schiller\\
L-414, LLNL\\
7000 East Avenue\\
Livermore, CA-94551}

\signature{Andreas Schiller}

\begin{letter}{Debbie Brodbar,\\
Assistant Editor\\
Physical Review C}

\opening{Re: CBR900 Schiller}

Dear Debbie Brodbar

Thank you very much for the referee report on our manuscript CBR900C\@. You 
will find our reply to the referee below.

Frankly, we do not think that the two reports of the referee constitute a fair
{\em scientific} and assessment of our work. Our main objection is that in 
general, the reports seem to us very opinionated. For example, to our mind, the
referee simply states that statistical assumptions are not justified for low 
excitation energies, where he arbitrarily defines 'low'. Already in our first 
reply, we have asked the referee to substantiate his claim with proper 
references to the scientific literature. Further, we have given him a list of 
references where statistical assumptions have been used with success at similar
excitation energies, and for the nuclei under study in our work. We were 
therefore very disappointed that in his second report the referee simply 
repeats his claim without any justification. We will give our arguments below 
in the comments why we believe the referee is wrong on this and other points.

In conclusion, despite our best efforts, we do not think that we can establish 
a constructive dialogue with the referee. We would therefore like to ask the 
editor if it is possible that the present manuscript be reviewed by a second 
referee.

\closing{Yours sincerely,}

\end{letter}

\end{document}