%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentstyle[12pt]{article}
\makeatletter
\topmargin 0pt
\ifcase \@ptsize
    \textheight 53\baselineskip
\or
    \textheight 46\baselineskip
\or
    \textheight 42\baselineskip
\fi
\advance\textheight by \topskip
\ifcase \@ptsize
    \textwidth      5.00in
    \marginparwidth 1.00in
  \if@twoside
    \oddsidemargin  0.55in
    \evensidemargin 0.75in
  \else
    \oddsidemargin  0.55in
    \evensidemargin 0.55in
  \fi
\or
    \textwidth      5.20in
    \marginparwidth 1.00in
  \if@twoside
    \oddsidemargin  0.45in
    \evensidemargin 0.65in
  \else
    \oddsidemargin  0.45in
    \evensidemargin 0.45in
  \fi
\or
    \textwidth      5.70in
    \marginparwidth 0.80in
  \if@twoside
    \oddsidemargin  0.20in
    \evensidemargin 0.40in
  \else
    \oddsidemargin  0.20in
    \evensidemargin 0.20in
  \fi
\fi
\def\WideMargins{%
  \newdimen\ExtraWidth
  \ifcase \@ptsize
    \ExtraWidth = 0.5in
    \@widemargins
  \or
    \ExtraWidth = 0.5in
    \@widemargins
  \or
    \ExtraWidth = 0.7in
    \@widemargins
  \fi\let\WideMargins\relax\let\@widemargins\relax}
{\def\do{\noexpand\do\noexpand}
 \xdef\@preamblecmds{\@preamblecmds \do\WideMargins}
}
\def\@widemargins{%
    \global\advance\textwidth by -\ExtraWidth
    \global\advance\marginparwidth by \ExtraWidth
    \if@twoside
      \tw@sidedwidemargins
    \else
      \@nesidedwidemargins
    \fi}
\def\tw@sidedwidemargins{%
    \if@reversemargin
      \@tempdima=\evensidemargin
      \advance\@tempdima by -\oddsidemargin
      \advance\oddsidemargin by \ExtraWidth
      \advance\oddsidemargin by \@tempdima
      \advance\evensidemargin by -\@tempdima
    \else
      \advance\evensidemargin by \ExtraWidth
    \fi}
\def\@nesidedwidemargins{%
    \if@reversemargin
      \advance\oddsidemargin by \ExtraWidth
      \advance\evensidemargin by \ExtraWidth
    \fi}
\makeatother

\newlength{\textwidtho}
\setlength{\textwidtho}{\textwidth}
\setlength{\topsep}{0pt}
\setlength{\headheight}{0pc}
\addtolength{\textwidth}{2pc}
\pagestyle{empty}
\setlength{\topmargin}{-3cm}
\setlength{\textheight}{29cm}

\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{-1.2cm}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35\baselineskip}
\begin{document}





\small

\underline{
\parbox{\textwidtho}{
\flushleft
{\sc elsevier science b.v.}
}}
\begin{flushleft}
{\large\bf  AUTHOR(S) OFFPRINT ORDER}\\[2ex]
\begin{tabular*}{\textwidth}
{@{\extracolsep{\fill}}p{0.5\textwidth}p{0.4\textwidth}}
{\bf Complete (even if you do not wish
to order additional  offprints) and return (FAX) immediately to:} \\
& \bf Article number: \\
{\small \bf Nuclear Physics}& \\
\footnotesize Elsevier Science B.V.& \bf Editorial Office number: \\
\footnotesize P.O. Box 103,&\bf \hfill NUCPHA
1099\\
1000 AC Amsterdam, The Netherlands       \\[1.5ex]
\footnotesize Telefax: +31 20 4852431      & \\
\footnotesize Office address for Courier Services:& {\LARGE $\boldmath 
       \rightarrow$} Please tick box {\LARGE $\boldmath \leftarrow$}  \\   
\footnotesize Sara Burgerhartstraat 25,    & {\Large $\boldmath\Box$} 
       I would like to receive proofs\\
\footnotesize 1055 KV Amsterdam, The Netherlands  &   {\Large 
       $\boldmath \Box$} I do not need to receive proofs% 
\end{tabular*}
\end{flushleft}

\begin{center}
\small \bf All offprints include covers
\end{center}

\small \bf Please supply me with: 


\framebox[0.5\textwidtho]{%
\parbox{0.5\textwidtho}{\protect\begin{center}
         {\protect\small\protect\bf  FREE}\\[5ex]
   50 offprints
   \protect\end{center}
                        }
}
\framebox[0.5\textwidtho]{%
\parbox{0.5\textwidtho}{\protect\begin{center}
         {\small\bf CHARGED  (minimum 100 extra)}\\[5ex]
   --- offprints
   \protect\end{center}
                        }
}

\begin{center}
\bf  For prices see Terms of Delivery
\end{center}


\bf Official Purchase Order No. \hrulefill\  



\footnotesize\bf Please quote your VAT Registration %\\[1.5ex]
Number (EU customers only) \hrulefill\  


\parbox[t]{0.5\textwidtho}{
\flushleft
\footnotesize Charge to:  (Complete Address)\\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[3ex]
Signature:
} %\vrule
\parbox[t]{0.5\textwidtho}{
\flushleft
\footnotesize Deliver to:  (Name and Complete Address) \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[1.5ex]
\ \hrulefill \ \\[3ex]
Date:
}

\begin{tabular*}{\textwidth}
{@{}@{\extracolsep{\fill}}p{0.3\textwidth}p{0.6\textwidth}}
\scriptsize $\Box$ {\bf Delivery by S.A.L.} (Surface Mail Air Lifted)&
\scriptsize at no extra charge to authors in: Argentina, Australia,
Brazil, Canada, China, Hong Kong,  India, Israel, Japan, Malaysia,
Mexico, New Zealand, Pakistan, Singapore, South Africa, South Korea, 
Taiwan, Thailand, U.S.A.\\ 
\multicolumn{2}{@{}p{0.95\textwidth}}{\scriptsize{\bf Attention:} authors  
       from other countries, please indicate below  whether you wish to 
       receive your paid offprints by airmail at 20\% extra or by surface 
       mail.} \\
\scriptsize $\Box$ {\bf Delivery by Surface Mail} & \scriptsize \bf no extra 
       charge.\\
\scriptsize $\Box$ {\bf Delivery by Airmail}      & \scriptsize \bf at 20\% 
       extra charge\\
\hline
\end{tabular*}


\scriptsize For Publisher's use, please leave blank.
\hfill
\begin{tabular}{lllllllllll}
  Vol./Issue    &&&&&& Page&& & To &\mbox{ }
\end{tabular}

\setlength{\parskip}{1\baselineskip}


\newpage
\underline{
\parbox{\textwidtho}{
\flushleft
{\normalsize \sc elsevier science b.v.}
}}

{\Large \bf TERMS OF DELIVERY}

\small
\begin{itemize}
\item[\bf 1.] These terms apply only to authors of articles appearing 
in this journal.

\item[\bf  2.] Offprints can be ordered by filling in the Author(s) Offprint 
Order Form and returning it to the Publisher. Offprints will only be 
supplied if this form is completed and returned. Receipt of offprint orders is not 
acknowledged.

\item[\bf 3.] All orders must be accompanied by an Institutional Purchase 
Order (unless they are prepaid). Delays can cause extra costs (see item 6).

\item[\bf 4.] Only one author receives an order form. It is essential that
the offprint requirements of all the authors of a paper are included on
this order form, as the price of offprints ordered after publication is 
substantially higher than those quoted here.

\item[\bf 5.] As typesetting costs are not included in offprint prices, any
blank page necessary to complete printer's forms will cost the same as a
printed page.

\item[\bf 6.] All plates are destroyed immediately after printing the issue 
unless offprints have been ordered. Offprint orders received late are treated 
as repeat orders; the price is then substantially higher.

\item[\bf 7.] Prices are subject to change without prior notice.

\item[\bf 8.] Cancellation of an order will not be accepted after the
printing of the journal has been finalized.

\item[\bf 9.] Claims for missing or damaged offprints must be made within 6
months from the date of our invoice.

\item[\bf 10.]  Any correspondence in connection with offprints must state
the name of the journal,  title and code number of the article, and name(s)
of the author(s).

\item[\bf 11.] Customers who are European Union residents should quote
their VAT registration number.

\end{itemize}

\vspace{1cm}

\begin{center}

{\bf Prices (excluding VAT) of offprints (in Dutch guilders).}

\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Number&\multicolumn{7}{c|}{Page length of article}& Additional\\
of copies &\multicolumn{7}{c|}{\hrulefill \ } &two\\
ordered&1-4&5-6&7-8&9-10&11-12&13-14&15-16&pages\\
\hline
\hline
100&306& 397& 488& 580& 671& 762& 854& 91\\
150&381& 487& 594& 701& 809& 915&1022&107\\
200&455& 576& 696& 817& 938&1059&1179&121\\
250&530& 663& 796& 928&1062&1195&1328&133\\
300&605& 750& 895&1040&1185&1330&1475&145\\
350&680& 837& 994&1151&1308&1465&1623&157\\
400&755& 924&1093&1262&1431&1601&1770&169\\
450&829&1011&1192&1373&1554&1736&1917&182\\
550&904&1098&1291&1484&1678&1871&2065&194\\
\hline
\hline
\multicolumn{9}{|c|}{\bf Rates for larger quantities are available on 
       request}\\
\hline
\end{tabular}

\end{center}

\newpage
\underline{
\parbox{\textwidtho}{
\flushleft
{\normalsize \sc elsevier science b.v.\hfill \small 
NUCPHA 1099}
}}

\begin{center}
{ \large\bf COPYRIGHT TRANSFER}
\end{center}
\small

Formal written transfer of copyright from the author(s) to the publisher is
required for each article. Such transfer enables the publisher to provide
for the widest possible dissemination of the article in printed, electronic
and other existing and future formats. Without this transfer of copyright,
such activities on the part of the publisher and the dissemination of
information may be limited. Transfer of copyright is also required to
enable the publisher to act against plagiarism and other forms of 
copyright infringement. We therefore ask that you complete and return this
form promptly. Your cooperation is essential and appreciated.


Copyright (including all rights thereunder and the right to obtain
copyrights registration in the name of the publisher, whether separately or
as part of a journal issue or otherwise) in the article (provisionally)
entitled:


{\it Self-energy of $\Lambda$ in finite nuclei}


to be published in the Journal {\bf Nuclear Physics A}


is hereby transferred, throughout the world and for the full term and all
extensions and renewals thereof, to:

\begin{center}
{\large\bf ELSEVIER SCIENCE B.V.}\\
\end{center}
{\footnotesize{

The author(s) reserve(s) trademark rights and patent rights, if any.


The author(s) may use all or part of the information contained in this
article in future, non-commercial works of the author's own, or, if the
article is a `work-for-hire' made within the scope of the author's
employment, the employer may use all or part of the information contained
in this article for intra-company use, provided acknowledgements are given
regarding copyright notice and reference to the original publication.


The author(s) warrant(s) that the article is the author(s)'s original work,
and has not been published before. If excerpts from copyrighted works are
included, the author(s) has obtained or will obtain written permission
from the copyright owners and shall credit the sources in the article. The
author(s) also warrant(s) that the article contains no libellous or
unlawful statements, and does not infringe on the rights of others.


If the article was prepared jointly with other author(s), the author has
informed the co-author(s) of the terms of this copyright transfer and is
signing on their behalf as their agent and represents that the author is
authorized to do so. In the case of an employed author(s) acting within
the scope of his employment (`work-for-hire') the employer or an
authorized representative of the employer must sign.


Signature of copyright owner:

(author or corporate representative) \dotfill \ 


Name (printed): \dotfill \ 

Date: \dotfill\  }} 

\rule[0.01cm]{\textwidth}{.05cm}\\ \hfill 
{\normalsize\it Please return this form* promptly to:

 ELSEVIER SCIENCE B.V.\\
\small
Nuclear Physics \\
P.O. Box 103, 1000 AC AMSTERDAM\\
THE NETHERLANDS
\begin{flushright}
\footnotesize {*We require the original signed form, not a faxed copy.}
\end{flushright}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




