\documentstyle[12pt]{article}
\begin{document}
\setlength{\parindent}{0cm} 
\setlength{\parskip}{2.0ex} 
\setlength{\parsep}{0ex} 
\pagestyle{plain}
MORTEN HJORTH-JENSEN\newline
ECT*, European Centre for Theoretical Studies in Nuclear\newline
Physics and Related areas, Villa Tambosi, Strada delle
Tabarelle 286, \newline I--38050 Villazzano (Trento), Italy\newline
phone: +39-461-314729/314730, Fax: +39-461-935007\newline
E-post: mhjensen@ect.unitn.it\newline
\vspace{2cm}
\hspace{5cm} Trento, December 3,  1995\newline
To: Sarah Quin, Assistant to the Editor

\begin{center} Revision of G/67897/PAP \end{center}


Dear Sarah Quin,

thanks a lot for your fax dated 29/nov/95 with referee reports.
In this letter you will find the revised version of the paper
following your instructions,  two copies of the amended version
and a list of changes made according to the suggestions of the referees.
The original figure is as before and is not included in this sending.
We haven't included comments  to the the referees, since we agree
fully with their proposals.

In addition, we have included a 3 1/2 inch disc, containing
the revised version of the paper. The file containing the source
code is called  PAPER.TEX. The Latex style used is that
of REVTex.

\begin{center} Yours sincerely \end{center}
\begin{center} Morten Hjorth-Jensen\end{center}

\clearpage

\begin{center} List of revisions made \end{center} 

\begin{enumerate}
\item Following referee 1, we have included after Eq. (4) a small paragraph
on single--particle insertions.
\item Following referee 1, we have also before Eq.\ (6) added
a discussion on the use of a fixed starting energy. In addition a
new reference (Ellis et al) is included.
\item We have removed
footnote 2, which created confusion. Real averages
are now presented in Tables 1 and 2. We have also changed the units, as proposed
by referee 1,  in tables 1 and
2 to keV, as it gives a better precision and may be of more
value to a possible reader. 
\item Eight lines after Eq. (7) we have corrected $V^(1)$ to
$V^{(1)}$ and $Q^2$ to $Q^{(2)}$.
\end{enumerate}

\end{document}






